The art of modelling the 3D structure of the genome\\ Insights in {\em P. falciparum} genome organization

### 2017-07-26 doc/manuscript/paper.tex
more rewording
bullet pointed the discussion

@@

In previous section, I have reviewed data-driven methods to infer either
\textit{consensus} or \textit{ensemble} models of the 3D structure. The reader
may well ask why go through the effort to obtain such model and not directly
study the contact maps?  In this section, I will review a number of downstream
analysis one can do on 3D models, highlighting but limiting myself to results
on the 3D structure of {\em P. falciparum}.

\subsection{Probing the 3D structure of the {\em P. falciparum}}
In the past year, two groups have published studies of {\em P.
falciparum}'s 3D genome architecture using Hi-C. \citet{lemieux:genome-wide}
studied several strains associated with populations expression unique
\textit{var} genes, in order to study key folding properties of the 3D
structure relating to \textit{var} gene expression. On the other hand,
\citet{ay:three-dimensional} focus three key time-point of the development
cycle. Table~\ref{tab:data} summarizes the available data sets and their key
properties after processing the data as described in
\citet{ay:three-dimensional} and combining all available libraries for each
life-cycle stage and strain.

@@

\fixme{Add the fact we have time points}

A substantial difficulty in modelling the 3D structure of the genome is that
model evaluation tends to the subjective. What is the relevant measure?
``Truth'' is generally not fully available, except for a few pairs of loci or
in simulations. Is validating the colocalization of a pair or a few pairs of
loci via FISH experiments enough? Is fit to the contact maps or agreements
between modeling techniques relevant?

\fixme{Add section on model evaluation}

@@

\subsection{Chromatin compaction}

@@

\section{Discussion}

@@

\begin{figure}[!p]
\centering
%\includegraphics{fig1}
\caption{}
\label{Fig1}
\end{figure}

>>>>

A substantial difficulty in modeling the 3D structure of the genome is that
model evaluation tends to the subjective. What is the relevant measure?
``Truth'' is generally not fully available, except for a few pairs of loci or
in simulations. Is validating the colocalization of a pair or a few pairs of
loci via FISH experiments enough? Is fit to the contact maps or agreements
between modeling techniques relevant?

@@

@@

In previous section, I have reviewed data-driven methods to infer either
\textit{consensus} or \textit{ensemble} models of the 3D structure. The reader
may well ask why go through the effort to obtain such model and not directly
study the contact maps?  \fixme{why?}In this section, I will review a number of downstream
analysis one can do on 3D models, highlighting but not limiting myself to results
on the 3D structure of {\em P. falciparum}. \fixme{why}

@@

\subsection*{Chromatin compaction}

@@

\section*{Discussion}

data-driven Plethora of methods, but only handfull that can be used on different
organisms and have been validated on simulated data set. Ensemble methods are
more challenging to use, to validate and to explore, but offer more
biologically accurate view of what is going on in teh nucleus. Overall,
powerfull tool but that still needs to be extended oto work on challenging
data set.

model-driven methods are organisms and study specific. For each data set, the
set of constraints need to be revisited. Yet, once built, they can be used ot
replace high throughput FISH experiments at low cost.

Downstream analysis gave important insights in the relation between gene
regulation and genome architecture of teh {\em P. falciparum}. Yet a lot
remains to be done. How to compare in a meaningful manner structures from
different time points at a genome-scale level?

@@
